---
title: "Great Virtual Run Across Tennessee"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    horizontal_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(rvest)
library(XML)
library(httr)
library(jsonlite)
library(DT)
library(lubridate)

df <- fromJSON("https://vacationwithoutacar.com/wp-admin/admin-ajax.php?action=wp_ajax_ninja_tables_public_action&table_id=3087&target_action=get-all-data")


df$position <- str_remove(df$position, "#")
# df$genplace <- str_remove(df$genplace, "#")


june <- paste0 ("June 01 - June ",substr((Sys.Date()-5), 9, 10) )

my_names <- c("Position", "Bib", "Name", "RAT Status", "RAT Finish", "Team", "Miles", "KM", "May", june, 
              as.character(Sys.Date() - 4), 
              as.character(Sys.Date() - 3), 
              as.character(Sys.Date() - 2), 
              as.character(Sys.Date() - 1), 
              as.character(Sys.Date())
              ) 

names (df) <- my_names

# names(df) <- names

updated <- read_html("https://vacationwithoutacar.com") %>% 
  html_node(".has-inline-color strong") %>% 
  html_text() 


df <- df %>% 
  mutate_at (c("Position", "Bib", "Miles", "KM"), as.numeric) 

df[7:12] <- map(df[7:12],
                as.numeric)

```

Column {.tabset} 
-------------------------------------

### Connors  (and others)


```{r}

connors <- c (1955, 17766, 2046, 17199, 15589, 370, 4591, 14971, 1738, 17200, 5507, 3996, 15689, 15675, 1969, 14517, 14633, 6139, 1629,
              10884, 15551, 1948, 2223, 1737, 2222, 1616, 6196, 1839, 2996, 107, 13227, 17963, 18091, 17741, 18927, 19314)

df_2 <- df %>% dplyr::filter (Bib %in% connors) %>% 
  mutate (`RAT Status` = parse_number(`RAT Status`)/100)

DT::renderDataTable (
  datatable(df_2 , #%>% select (names_select), 
            options = list(pageLength = 40)
            ) %>% 
    DT::formatPercentage("RAT Status", 
                         digits = 1)
   
)

```


### All Runners

These standings will be posted every 2-4 hours until we get the live tracking up and running. `r updated`. 


```{r}


DT::renderDataTable (
  
  datatable(df 
            )
)


```


<!-- ### Connors (and others) Over Time -->

<!-- ```{r} -->

<!-- runners_names <- sort (df_2$Name) -->

<!-- selectInput("runner",  -->
<!--             "Runner", -->
<!--             choices = c("All", runners_names) -->
<!--             )   -->

<!-- ``` -->

<!-- ```{r} -->


<!-- p <- reactive({ -->

<!--   if(input$runner == "All") -->

<!--     p <- df_2 %>% -->
<!--       ggplot(aes(ranking , group = Name, color=Name,fill=Name)) + -->
<!--       geom_tile(aes(y = cumsum / 2, -->
<!--                     height = cumsum, -->
<!--                     width = 0.9), alpha = 0.9) + -->
<!--       geom_text(aes(y = -5 + cumsum, x = ranking, label = Name), -->
<!--                 hjust = 1, -->
<!--                 colour = "black") + -->
<!--       geom_text(aes(y = cumsum + 5, x = ranking, label = as.character(cumsum)), -->
<!--                 colour = "black") + -->
<!--       coord_flip(clip = "off", expand = FALSE) + -->
<!--       scale_y_continuous(limits = c (0, max(temp$cumsum + 25))) + -->
<!--       guides(color = FALSE, fill = FALSE)+ -->
<!--       labs(title='{frame_time}', x = "",y="Miles") + -->
<!--       theme(plot.title = element_text(hjust = 1, size = 22), -->
<!--             axis.ticks.y = element_blank(), -->
<!--             axis.text.y  = element_blank(), -->
<!--             panel.background = element_rect(fill = "white"), -->
<!--             plot.margin = margin(1, 1, 1, 3, "cm"), -->
<!--             plot.background = element_rect( -->
<!--               fill = "white", -->
<!--               colour = "white", -->
<!--               size = 1)) + -->
<!--       transition_time(Day) + -->
<!--       ease_aes('cubic-in-out')  -->


<!--   }) -->



```

```{r include=FALSE}

library(lubridate)

name <- "Brian Schmidt"

temp <- df_2 %>% 
  select (Name, starts_with(c("May", "June"))) %>% 
  pivot_longer(-Name, 
               names_to = "Day",
               values_to = "Miles") %>% 
  mutate (Day = str_replace(Day, "May ", "05-")) %>% 
  mutate (Day = paste0 ("2020-", Day)) %>% 
  mutate (Day = ymd(Day)) %>% 
  group_by (Name) %>% 
  mutate (cumsum = cumsum (Miles)) %>% 
  mutate (group = ifelse (Name == name, "1", "0")) 

temp <- temp  %>% 
  group_by (Day) %>% 
  dplyr::mutate (ranking = rank (cumsum, ties.method = "first")) %>% 
  arrange (Day, desc(ranking)) 

library(gganimate)

# All Runners
# temp %>%
#   ggplot(aes(ranking , group = Name, color=Name,fill=Name)) +
#   geom_tile(aes(y = cumsum / 2,
#                 height = cumsum,
#                 width = 0.9), alpha = 0.9) +
#   geom_text(aes(y = -5 + cumsum, x = ranking, label = Name),
#             hjust = 1,
#             colour = "black") +
#   geom_text(aes(y = cumsum + 5, x = ranking, label = as.character(cumsum)),
#             colour = "black") +
#   coord_flip(clip = "off", expand = FALSE) +
#   scale_y_continuous(limits = c (0, max(temp$cumsum + 25))) +
#   guides(color = FALSE, fill = FALSE)+
#   labs(title='{frame_time}', x = "",y="Miles") +
#   theme(plot.title = element_text(hjust = 1, size = 22),
#         axis.ticks.y = element_blank(),
#         axis.text.y  = element_blank(),
#         panel.background = element_rect(fill = "white"),
#         plot.margin = margin(1, 1, 1, 3, "cm"),
#         plot.background = element_rect(
#           fill = "white",
#           colour = "white",
#           size = 1)) +
#   transition_time(Day) +
#   ease_aes('cubic-in-out')

# Select Runner
# p <- temp %>%
#   mutate (Month = month (Day, label = TRUE),
#           Day_R = day (Day),
#           new_label = paste0 (Month, " ", Day_R)) %>%
#   ggplot(aes(ranking , group = group, fill=group)) +
#   geom_tile(aes(y = cumsum / 2,
#                 height = cumsum,
#                 width = 0.9), alpha = 0.9) +
#   geom_text(aes(y = -5 + cumsum, x = ranking, label = Name),
#             hjust = 1,
#             colour = "black") +
#   geom_text(aes(y = cumsum + 5, x = ranking, label = as.character(cumsum)),
#             colour = "black") +
#   coord_flip(clip = "off", expand = FALSE) +
#   scale_fill_manual(values = c("#2780E3", "grey80" )) +
#   scale_y_continuous(limits = c (0, max(temp$cumsum + 25))) +
#   guides(color = FALSE, fill = FALSE)+
#   labs(title='{frame_time}', x = "",y="Miles") +
#   theme(plot.title = element_text(hjust = 1, size = 22),
#         axis.ticks.y = element_blank(),
#         axis.text.y  = element_blank(),
#         panel.background = element_rect(fill = "white"),
#         plot.margin = margin(1, 1, 1, 3, "cm"),
#         plot.background = element_rect(
#           fill = "white",
#           colour = "white",
#           size = 1)) +
#   transition_time(Day) +
#   ease_aes('cubic-in-out')
# 
# animate(p, nframes = 150, fps = 10, end_pause = 20, width = 900, height = 900)#+

# p <- Cumulative.long %>%
#     ggplot(aes(x = -DailyRank,y = CumulativeCase, group = PHU)) +
#         geom_tile(aes(y = CumulativeCase / 2, height = CumulativeCase, fill = PHU), width = 0.9) +
#         geom_text(aes(label = PHU), hjust = "right", colour = "black", fontface = "bold", nudge_y = -10) +
#         geom_text(aes(label = scales::comma(CumulativeCase)), hjust = "left", nudge_y = 10, colour = "grey30") +
#         coord_flip(clip="off") +
#         scale_x_discrete("") +
#         scale_y_continuous("",labels=scales::comma) +
#         hrbrthemes::theme_ipsum(plot_title_size = 32, subtitle_size = 24, caption_size = 20, base_size = 20) +
#         theme(panel.grid.major.y=element_blank(),
#               panel.grid.minor.x=element_blank(),
#               legend.position = "none",
#               plot.margin = margin(1,1,1,8,"cm"), #top, right, bottom, left
#               axis.text.y=element_blank()) +
#         # gganimate code to transition by year:
#         transition_time(Accurate_Episode_Date) +
#         ease_aes('cubic-in-out') +
#         labs(title='Public Health Units',
#              subtitle='Number of COVID19 Cases reported {round(frame_time,0)}',
#              caption='Source: data.ontario.ca
# DUGroup.ca / @ResearchChat')
# animate(p, nframes = 750, fps = 30, end_pause = 50, width = 1200, height = 900)#+


```

